\section{Pre-session preparation}
\subsection{Installing Python}
	Complete the instructions in this first section before attending the first session.
	
	We assume you are either using a Windows or Mac PC. If you are running Linux then you can probably work it out for yourself! A basic understanding of the terminal (mac) or command prompt (windows) is assumed. If not then Google a tutorial. We assume that you have not previously installed a Python 3 distribution to your system.
	
	Download the Anaconda Python 3.5 distribution from \url{https://www.continuum.io/downloads}. This includes the Python language as well as useful libraries and tools. Install following the instructions and accepting default values.

	Open a terminal window (mac) or command prompt (Windows). Navigate (using the "cd" command to navigate the file system) to an empty directory (I suggest somewhere in My Documents) where you want to store files generated in these lectures. Type:
	\begin{verbatim}
		ipython notebook
	\end{verbatim}

After a few moments this should open a window in your internet browser. In the top right hand corner click "new" and under notebooks select Python 3. This should open a Python notebook. This is an interactive Python session where your code is input into "cells" on the page. Once you have written some code in a cell, press the "Shift" and "Return" keys simultaneously to execute the code in the cell.

To test your distribution has installed correctly type the following into a cell and execute it:

		\begin{lstlisting}[language=Python]
import numpy as np
print("Hello World")\end{lstlisting}
		\begin{verbatim}> Hello World\end{verbatim}
		
In this tutorial, the numbered code on the light grey background is code that you should execute. Bold text is the expected output from that code.

\textbf{Ensure that this works correctly before attending the first session.} If in doubt, collaborate with one of your colleagues also taking this course to get it working.


\subsection{Installing Ovito}

Once we have created done some simulations it is nice to be able to visualise the trajectories of the particles. We will do this using some software called Ovito. Download from: \url{http://www.ovito.org/index.php/download}. The program does not need installing as such, just unzip it and run from the folder.